The Name of the Title Is Hope

### 2024-12-30 paper.tex
Remove duplicate paragraph

\subsection{The Scan Primitive}
The study of \emph{scan} (\emph{parallel prefix}) networks traces back to the design of carry-lookahead adder circuits and beyond~\cite{10.1145/322217.322232, 5219801}. A scan is typically defined on a monoid \( M \), characterized by a binary reduction operator \( \oplus \) and an identity element \( \varepsilon \). The binary operator \( \oplus \) satisfies the closure property \( \forall a, b \in M, \ (a \oplus b) \in M \) and has an identity element \( \exists \varepsilon \in M, \ \forall a \in M, \ \varepsilon \oplus a = a \). Although \( \oplus \) must be associative, it is not necessarily commutative, as demonstrated in structures like the stack monoid~\cite{}. In a scan, the result at the \( n \)-th element is the reduction of the preceding subset of elements in the sequence. If the subset includes the \( n \)-th element, it is called \textit{inclusive}; if it excludes the \( n \)-th element, it is called \textit{exclusive}. The most common scan type is the prefix sum, where \( \oplus \) is addition. For example:
\[
  x = [x_1, x_2, x_3, \dots, x_n] \ \ \ \ \ \ \ y = [1, 1, 1, 1, 1] 
\]
\[
  \text{InclusiveScan}(x, \oplus) = [x_1, x_1 \oplus x_2, x_1 \oplus x_2 \oplus x_3, \dots, x_1 \oplus x_2 \oplus \cdots \oplus x_n]
\]
\[
  \text{InclusiveScan}(y, +) = [1, 2, 3, 4, 5]
\]

Due to its significance in circuits and as a fundamental algorithmic primitive, scan enjoys a rich literature in both electrical engineering and computer science. Harris provides a taxonomy relating depth, fanout, and wire tracks. Hinze provides an algebra of scans. Snir proved that depth and size are related by . Fich proved that . Merill and Garland provide a comprehensive review of GPU scan implementations in . In light of this work(reword this), our focus is on exploring the progression of inter-workgroup (global) scan strategies and their fitness relative to our ideal architecture.

Due to its significance in circuits and as a fundamental algorithmic primitive, scan has been extensively studied in both electrical engineering and computer science. Harris offers a taxonomy that relates depth, fanout, and wire tracks~\cite{}, while Hinze develops an algebraic framework for scans~\cite{}. Snir proved that \emph{depth} and \emph{size} are related by (fill in)~\cite{}, and Fich proved that among minimum depth scans Ladner-Fischer networks have optimal size. Finally, Merrill and Garland provide a comprehensive review of GPU scan implementations. In this work, we focus on the evolution of inter-workgroup (global) scan strategies and evaluate their suitability for our ideal architecture.

>>>>

\subsection{The Scan Primitive}
The study of \emph{scan} (\emph{parallel prefix}) networks traces back to the design of carry-lookahead adder circuits and beyond~\cite{10.1145/322217.322232, 5219801}. A scan is typically defined on a monoid \( M \), characterized by a binary reduction operator \( \oplus \) and an identity element \( \varepsilon \). The binary operator \( \oplus \) satisfies the closure property \( \forall a, b \in M, \ (a \oplus b) \in M \) and has an identity element \( \exists \varepsilon \in M, \ \forall a \in M, \ \varepsilon \oplus a = a \). Although \( \oplus \) must be associative, it is not necessarily commutative, as demonstrated in structures like the stack monoid~\cite{}. In a scan, the result at the \( n \)-th element is the reduction of the preceding subset of elements in the sequence. If the subset includes the \( n \)-th element, it is called \textit{inclusive}; if it excludes the \( n \)-th element, it is called \textit{exclusive}. The most common scan type is the prefix sum, where \( \oplus \) is addition. For example:
\[
  x = [x_1, x_2, x_3, \dots, x_n] \ \ \ \ \ \ \ y = [1, 1, 1, 1, 1] 
\]
\[
  \text{InclusiveScan}(x, \oplus) = [x_1, x_1 \oplus x_2, x_1 \oplus x_2 \oplus x_3, \dots, x_1 \oplus x_2 \oplus \cdots \oplus x_n]
\]
\[
  \text{InclusiveScan}(y, +) = [1, 2, 3, 4, 5]
\]
Due to its significance in circuits and as a fundamental algorithmic primitive, scan has been extensively studied in both electrical engineering and computer science. Harris offers a taxonomy that relates depth, fanout, and wire tracks~\cite{}, while Hinze develops an algebraic framework for scans~\cite{}. Snir proved that \emph{depth} and \emph{size} are related by (fill in)~\cite{}, and Fich proved that among minimum depth scans Ladner-Fischer networks have optimal size. Finally, Merrill and Garland provide a comprehensive review of GPU scan implementations. In this work, we focus on the evolution of inter-workgroup (global) scan strategies and evaluate their suitability for our ideal architecture.
